Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-22 awipev-CO2.Rmd
all variables updated

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered, temp_durafet = HW_Temperature1_filtered, temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)

d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_hour TO d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_insitu_ctd)), by="closest_datetime")

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_ctd = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_insitu_ctd,Pt=0,Sit=0))

@@

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_ctd)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_ctd = mean(pH_s_seafet_temp_ctd, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_fb = mean(pH_s_durafet_temp_fb, na.rm = T))

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_ctd) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

d_all <- d_all%>%
  dplyr::mutate(depth = ifelse(pressure_insitu_ctd_filtered <=2, "1 m", 
                        ifelse(pressure_insitu_ctd_filtered >2 & pressure_insitu_ctd_filtered <=4, "3 m", 
                        ifelse(pressure_insitu_ctd_filtered >4 & pressure_insitu_ctd_filtered <=6, "5 m",
                        ifelse(pressure_insitu_ctd_filtered >6 & pressure_insitu_ctd_filtered <=8, "7 m",
                        ifelse(pressure_insitu_ctd_filtered >8, "9 m",NA))))))
```

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
                               ifelse (pressure_insitu_ctd_filtered >=8 ,sal_insitu_ctd, NA )))
### remove sal_mix datat that seem to be to high compared to sal_fb
  d_all <- d_all%>%
  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
                          ifelse(datetime > "2018-05-28 06:00:00" & datetime < "2018-06-03 13:00:00" , NA,
                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
                               ifelse (pressure_insitu_ctd_filtered >=8 ,temp_insitu_ctd, NA )))
```

@@

#SAL MIX

@@

dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD)", ylab="Salinity") %>%

@@

@@

pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)

@@

    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
      dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb)

@@

    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd)

@@

  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

@@

p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_point( aes(color=factor(datetime_chr))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
   scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()

@@

```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
  dyLegend(show = "onmouseover")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  dyAxis( "y2",valueRange = c(25, 36))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)

@@

```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
#Interpolation of continuous sensor data to match a maximum of reference data.
TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
TAinterp_all <- as.data.frame(TAinterp_all)
d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp

# create a column with difference between sensor and ref
d_all <- d_all%>%
  dplyr::mutate(diff_ta =  at-AT_filtered_interp )
# create colum with instrument number
d_all <- d_all %>%
  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour_copy.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

d_all <- d_all%>%
  dplyr::mutate(depth = ifelse(pressure_insitu_ctd <=2, "1 m", 
                        ifelse(pressure_insitu_ctd >2 & pressure_insitu_ctd <=4, "3 m", 
                        ifelse(pressure_insitu_ctd >4 & pressure_insitu_ctd <=6, "5 m",
                        ifelse(pressure_insitu_ctd >6 & pressure_insitu_ctd <=8, "7 m",
                        ifelse(pressure_insitu_ctd >8, "9 m",NA))))))
```

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
                               ifelse (pressure_insitu_ctd >=8 ,sal_insitu_ctd, NA )))
### remove sal_mix data that seem to be to high compared to sal_fb
  d_all <- d_all%>%
  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
                          ifelse(datetime > "2018-05-29 15:00:00" & datetime < "2018-06-03 13:00:00" , NA,
                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
                               ifelse (pressure_insitu_ctd >=8 ,temp_insitu_ctd, NA )))
```

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_mix, temp_insitu_ctd, temp_insitu_11m, sal_mix )), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_mix)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_mix = mean(pH_s_seafet_temp_mix, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_fb = mean(pH_s_durafet_temp_fb, na.rm = T))

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_mix) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

@@

#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb)
dygraph(sal_xts, group = "awipev", main="Salinities (in situ CTD, all depths + FB)", ylab="Salinity") %>%
      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "CTD") %>%
            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "FB") %>%
#SAL FB

@@

dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%

@@

# TEMP insitu CTD
temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd)
dygraph(temp_insitu_xts, group = "awipev", main="Temperature (ctd all depths)", ylab="Temperature") %>%
      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "T") %>%

@@

pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_corr)

@@

    dySeries("pco2_corr", label="Corrected pCO2", color=  "blue",strokeWidth=0, pointSize=2) %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, pH_s_durafet_temp_fb)

@@

    dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,pH_s_seafet_temp_mix)

@@

  dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pH_s_seafet_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
  dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

@@

p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_point( aes(color=factor(datetime_chr))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
   scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()

@@

```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
#dySeries("pressure_insitu_ctd", label = "pressure_insitu_ctd", color ="black", strokeWidth=0, pointSize=2) %>%
  dyLegend(show = "onmouseover")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y2",valueRange = c(25, 36))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)

@@

```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
#Interpolation of continuous sensor data to match a maximum of reference data.
TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2)
names(TAinterp_all) <- c("datetime", "AT_interp")
TAinterp_all <- as.data.frame(TAinterp_all)
d_all$AT_interp <- TAinterp_all$AT_interp

# create a column with difference between sensor and ref
d_all <- d_all%>%
  dplyr::mutate(diff_ta =  at-AT_interp )
# create colum with instrument number
d_all <- d_all %>%
  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))

#remove outliers
calib_ta_first <- d_all%>%
  dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>%
  dplyr::filter(TA_period =="TA1" & !is.na(at))
  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
